---
title: "Quantium - Retail Strategy and Analysis - Task 1"
mainfont: Georgia
monofont: Courier New
output:
  html_document: 
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
# set options for R markdown knitting
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(linewidth=80)
```

```{r knitr line wrap setup, include=FALSE}
# set up line wrapping in MD knit output
library(knitr)
hook_output = knit_hooks$get("output")
knit_hooks$set(output = function(x, options)
{
    # this hook is used only when the linewidth option is not NULL
    if (!is.null(n <- options$linewidth))
    {
        x = knitr:::split_lines(x)
        # any lines wider than n should be wrapped
        if (any(nchar(x) > n))
            x = strwrap(x, width = n)
        x = paste(x, collapse = "\n")
    }
    hook_output(x, options)
})

```

## Load required libraries and data sets

Note that you will need to install these libraries if you have never used these before.

```{r 0 Load Libraries, results = 'hide'}
#### Example code to install packages
#install.packages("data.table")

#### Load required libraries
library(data.table)
library(ggplot2)
library(ggmosaic)
library(readr)
library(skimr)
library(here)
# library(dplyr)

filePathTXN <- 
#### Import data
transactionData <- fread(here("data","QVI_transaction_data.csv"))
customerData <- fread(here("data","QVI_purchase_behaviour.csv"))
```

## Exploratory data analysis

The first step in any analysis is to first understand the data. Let's take a look at each of the data sets provided.

### Examining transaction data

We can use `str()` to look at the format of each column and see a sample of the data. As we have read in the dataset as a `data.table` object, we can also run `transactionData` in the console to see a sample of the data or use `head(transactionData)` to look at the first 10 rows.

Let's check if columns we would expect to be numeric are in numeric form and date columns are in date format.

```{r Examining transaction data}
#### Examine transaction data
str(transactionData)
head(transactionData)
summary(transactionData)

# expected numeric columns are indeed numeric
```

We can see that the date column is in an integer format. Let's change this to a date format.

```{r Convert DATE to date format}
#### Convert DATE column to a date format
#### A quick search online tells us that CSV and Excel integer dates begin on 30
#### Dec 1899
transactionData$DATE <- as.Date(transactionData$DATE, origin = "1899-12-30")

```

We should check that we are looking at the right products by examining PROD_NAME.

```{r Summary of PROD_NAME}
#### Examine PROD_NAME by generating a summary of the PROD_NAME column
levels(as.factor(transactionData$PROD_NAME))
prod_counts <- table(transactionData$PROD_NAME)

# count of unique products
length(unique(transactionData$PROD_NAME))

# most common product
names(prod_counts)[which.max(prod_counts)]
# freq of the most common product
max(prod_counts)

# frequency of occurrence for the top ten products
head(sort(prod_counts,decreasing = TRUE),n = 10)


# sort(summary.factor(transactionData[, PROD_NAME]), decreasing = TRUE)

```

Looks like we are definitely looking at potato chips but how can we check that these are all chips? We can do some basic text analysis by summarizing the individual words in the product name.

```{r Further examine PROD_NAME}
#### Examine the words in PROD_NAME to see if there are any incorrect entries
#### such as products that are not chips

# split product names of the string unique(transactionData[, PROD_NAME])
# then unlist the list of vectors into a single vector
# then it into a data.table object
productWords <- data.table(unlist(strsplit(unique(transactionData[, PROD_NAME]), "\t"))) 
setnames(productWords, 'words')
productWords

```

```{r}
# play around
head(unique(transactionData[, PROD_NAME]))

# play around
head(strsplit(unique(transactionData[, PROD_NAME]), "\t"))
# this is a list of vectors
# [[1]] means the first element in this list, [[2]] second element and so on
# [1] means the first element within the first vector

head(transactionData$PROD_NAME)

```

As we are only interested in words that will tell us if the product is chips or not, let's remove all words with digits and special characters such as '&' from our set of product words. We can do this using `grepl()`.

```{r}

# Remove digits, and special characters, and then sort the distinct
# words by frequency of occurrence.

# str(productWords) to recall what object we are working with

#### Removing digits
# productWordsd is a data.table with one column 'words'
# regex "\\d+g$" matches one or more digits followed by any character at the end of every word
# gsub fucnction then replaces pattern with empty string
productWords[, words := gsub("\\d+.$", "", words)]

# note the := operator is specific to the data.table package. 
# it is used to update or assign values to columns within a data.table object. 

#### Removing special characters
productWords[, words := gsub("\\W+", " ", words)]

#### Let's look at the most common words by counting the number of times a word
# appears and sorting them by this frequency in order of highest to lowest frequency
sort(table(unlist(strsplit(unique(productWords[, words]), " "))), decreasing = TRUE)

```

There are salsa products in the dataset but we are only interested in the chips category, so let's remove these.

```{r}
#### Remove salsa products
# 1) identify rows that are salsa products
# 2) remove these rows

# helpful to recall data.table structure
# DT[i, j, by]
##   R:                 i                 j        by
## SQL:  where | order by   select | update  group by

# create a new column 'SALSA' containing logical values
# to identify rows that have the word 'salsa' in PROD_NAME
# use tolower to standardize the word 'salsa'
transactionData[, SALSA := grepl("salsa", tolower(PROD_NAME))]
# [SALSA == FALSE, ] selects only rows that are not salsa products
# then [, SALSA := NULL] deletes the 'SALSA' column
transactionData <- transactionData[SALSA == FALSE, ][, SALSA := NULL]

```

Next, we can use `summary()` to check summary statistics such as mean, min and max values for each feature to see if there are any obvious outliers in the data and if there are any nulls in any of the columns (`NA's : number of nulls` will appear in the output if there are any nulls).

```{r initial summary}
#### Summarise the data to check for nulls and possible outliers
summary(transactionData)

```

There are no nulls in the columns but product quantity appears to have an outlier which we should investigate further. Let's investigate further the case where 200 packets of chips are bought in one transaction.

```{r }
#### Filter the dataset to find the outlier
transactionData[PROD_QTY == "200"]

```

There are two transactions where 200 packets of chips are bought in one transaction and both of these transactions were by the same customer.

```{r}
#### Let's see if the customer has had other transactions
transactionData[LYLTY_CARD_NBR == "226000"]

```

It looks like this customer has only had the two transactions over the year and is not an ordinary retail customer. The customer might be buying chips for commercial purposes instead. We'll remove this loyalty card number from further analysis.

```{r}
#### Filter out the customer based on the loyalty card number
transactionData <- transactionData[LYLTY_CARD_NBR != "226000"]

#### Re-examine transaction data
summary(transactionData)

```

That's better. Now, let's look at the number of transaction lines over time to see if there are any obvious data issues such as missing data.

```{r}
# this part works on performing operations by group

#### Count the number of transactions by date
transaction_count <- transactionData[, .N, by = DATE]
transaction_count
```

There's only 364 rows, meaning only 364 dates which indicates a missing date. Let's create a sequence of dates from 1 Jul 2018 to 30 Jun 2019 and use this to create a chart of number of transactions over time to find the missing date.

```{r fig.align = "center"}
#### Create a sequence of dates and join this onto the count of transactions by date

# create a column of dates that includes every day from 1 Jul 2018 to
# 30 Jun 2019, then join it onto the data to fill in the missing day.

# use this format seq(start_date, end_date, by = "day")
date_seq <- seq(as.Date("2018-7-1"), as.Date("2019-6-30"), by = "day")
# convert date_seq to data.table
date_seq_dt <- data.table(DATE = date_seq)

# perform a right join between transaction count and date sequence
# a right join is a type of database join operation that combines two tables based on a common column, 
# while including all rows from the right table and matching rows from the left table
# right table in this case is date_seq_dt
transactions_by_day <- merge.data.table(transaction_count,date_seq_dt, 
                                        by = "DATE", all.y = TRUE)
# or we can do transaction_count[date_seq_dt, on = "DATE"] but this is a bit less intuitive


#### Setting plot themes to format graphs
theme_set(theme_bw())
theme_update(plot.title = element_text(hjust = 0.5))

#### Plot transactions by date
ggplot(transactions_by_day, aes(x = DATE, y = N)) +
  geom_line() +
  labs(x = "Day", y = "Number of transactions", title = "Transactions over time") +
  scale_x_date(breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

We can see that there is an increase in purchases in December and a break in late December. Let's zoom in on this.

```{r fig.align = "center"}
#### Filter to December and look at individual days

# Over to you - recreate the chart above zoomed in to the relevant dates.
ggplot(transactions_by_day[DATE %like% "-12-", ], aes(x = DATE, y = N)) +
  geom_line() +
  labs(x = "Day", y = "Number of transactions", title = "Transactions over time") +
  scale_x_date(breaks = "1 day") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

```

We can see that the increase in sales occurs in the lead-up to Christmas and that there are zero sales on Christmas day itself. This is due to shops being closed on Christmas day.

Now that we are satisfied that the data no longer has outliers, we can move on to creating other features such as brand of chips or pack size from PROD_NAME. We will start with pack size.

```{r Create pack size}
#### Pack size
#### We can work this out by taking the digits that are in PROD_NAME
transactionData[, PACK_SIZE := parse_number(PROD_NAME)]

#### Always check your output
#### Let's check if the pack sizes look sensible
transactionData[, .N, PACK_SIZE][order(PACK_SIZE)]

```

The largest size is 380g and the smallest size is 70g - seems sensible!

```{r }
#### Let's plot a histogram of PACK_SIZE since we know that it is a categorical
# variable and not a continuous variable even though it is numeric.

# plot a histogram showing the number of transactions by pack size.
ggplot(transactionData, aes(x = PACK_SIZE)) +
  geom_histogram(bins = 20)
```

Pack sizes created look reasonable.

Now to create brands, we can use the first word in PROD_NAME to work out the brand name...

```{r Create brand name}
#### Brands
# Over to you! Create a column which contains the brand of the product, by
# extracting it from the product name.


# Extract brand name from PROD_NAME
transactionData[, BRAND := sub("^([A-Za-z]+).*", "\\1", PROD_NAME)]
# '^([A-Za-z]+)' matches and captures one or more consecutive alphabetic characters at the start of the string.
# '.*' matches any remaining characters in the string.
# '\\1' is the replacement string that refers to the captured group (brand name).



# another way to write
# transactionData$Brand <- gsub("^(\\S+).*", "\\1", transactionData$PROD_NAME)

# another (long) way, using loop to iterate through PROD_NAME and apply a function to extract brand name
# transactionData[, BRAND := unlist(lapply(transactionData$PROD_NAME,
#                                          FUN = function(x){unlist(strsplit(x," "))[1]}))]



#### Checking brands
# check to see if the results look reasonable.
head(transactionData$BRAND)

```

Some of the brand names look like they are of the same brands - such as RED and RRD, which are both Red Rock Deli chips. Let's combine these together.

```{r Clean brand names}
#### Clean brand names
transactionData[BRAND %in% c("RED", "Red"), BRAND := "RRD"]
transactionData[BRAND == "Dorito", BRAND := "Doritos"]
transactionData[BRAND == "Smith", BRAND := "Smiths"]
transactionData[BRAND == "Snbts", BRAND := "Sunbites"]
transactionData[BRAND == "WW", BRAND := "Woolworths"]

# transactionData[BRAND == "GrnWves", BRAND := "Sunbites"] maybe?

#### Check to see if the results look reasonable
table(transactionData$BRAND)
```

### Examining customer data

Now that we are happy with the transaction dataset, let's have a look at the customer dataset.

```{r 1 Exploratory data analysis}

#### Examining customer data
str(customerData)
skim(customerData)

# distributions of columns
sort(table(customerData$LIFESTAGE), decreasing = TRUE)
sort(table(customerData$PREMIUM_CUSTOMER), decreasing = TRUE)

```

```{r }
#### Merge transaction data to customer data
data <- merge(transactionData, customerData, all.x = TRUE)

```

As the number of rows in `data` is the same as that of `transactionData`, we can be sure that no duplicates were created. This is because we created `data` by setting `all.x = TRUE` (in other words, a left join) which means take all the rows in `transactionData` and find rows with matching values in shared columns and then joining the details in these rows to the `x` or the first mentioned table.

Let's also check if some customers were not matched on by checking for nulls.

```{r Check for missing customer details}

# check if any transactions did not have a matched customer.
skim(data)
# to only specifically check for nulls
sapply(data, function(x) sum(is.na(x)))
```

Great, there are no nulls! So all our customers in the transaction data has been accounted for in the customer dataset.

Note that if you are continuing with Task 2, you may want to retain this dataset which you can write out as a csv

```{r Code to save dataset as a csv}
fwrite(data, here("data","QVI_data.csv"))
```

Data exploration is now complete!

## Data analysis on customer segments

Now that the data is ready for analysis, we can define some metrics of interest to the client:

-   Who spends the most on chips (total sales), describing customers by lifestage and how premium their general purchasing behaviour is
-   How many customers are in each segment
-   How many chips are bought per customer by segment
-   What's the average chip price by customer segment

We could also ask our data team for more information. Examples are:

-   The customer's total grocery spend over the period and total spend for each chips transaction to understand what proportion of their grocery spend is on chips
-   Proportion of customers in each customer segment overall to compare against the mix of customers who purchase chips

Let's start with calculating total sales by LIFESTAGE and PREMIUM_CUSTOMER and plotting the split by these segments to describe which customer segment contributes most to chip sales.

```{r fig.width = 10, fig.align = "center"}
#### calculate Total sales by LIFESTAGE and PREMIUM_CUSTOMER and create a plot
sales <- data[, .(SALES = sum(TOT_SALES)), .(LIFESTAGE, PREMIUM_CUSTOMER)]

#### Create plot
p <- ggplot(data = sales) +
  # weight = SALES means that the size or area of each mosaic tile will be proportional to the corresponding sales value. 
  # product() is used to create a combined factor variable that represents different combinations of PREMIUM_CUSTOMER and LIFESTAGE
  geom_mosaic(aes(weight = SALES, x = product(PREMIUM_CUSTOMER, LIFESTAGE), fill = PREMIUM_CUSTOMER)) +
  labs(x = "Lifestage", y = "Premium customer flag", title = "Proportion of sales") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
# The labels are generated by calculating the proportion of each tile's weight (SALES) 
# relative to the sum of all weights in the plot.
p + geom_text(data = ggplot_build(p)$data[[1]], 
              # ggplot_build(p)$data is a list of layers that contains the data used to create the layers in a ggplot object p.
              aes(x = (xmin + xmax)/2 , # this is to position the text 
                  y = (ymin + ymax)/2,  # in the middle of each tile
                  label = as.character(paste(round(.wt/sum(.wt),3)*100, '%'))))

```

Note that the percentage of each tile is relative to the total sales.

Sales are coming mainly from Budget - older families, Mainstream - young singles/couples, and Mainstream - retirees

Let's see if the higher sales are due to there being more customers who buy chips.

```{r fig.width = 10, fig.align = "center"}
#### Calculate Number of customers by LIFESTAGE and PREMIUM_CUSTOMER and create a plot.
# uniqueN is equivalent to length(unique(x))
customers <- data[, .(CUSTOMERS = uniqueN(LYLTY_CARD_NBR)), .(LIFESTAGE, PREMIUM_CUSTOMER)][order(-CUSTOMERS)]
 
p <- ggplot(data = customers) +
  geom_mosaic(aes(weight = CUSTOMERS, x = product(PREMIUM_CUSTOMER,LIFESTAGE), fill = PREMIUM_CUSTOMER)) +
  labs(x = "Lifestage", y = "Premium customer flag", title = "Proportion of customers") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p + geom_text(data = ggplot_build(p)$data[[1]], 
              aes(x = (xmin + xmax)/2 , 
                  y = (ymin + ymax)/2, 
                  label = as.character(paste(round(.wt/sum(.wt),3)*100,'%'))))
# .wt refers to the weight variable specified in 'weight' aesthetic of the geom_mosaic() layer


ggplot(customers, aes(x = LIFESTAGE, y = CUSTOMERS, fill = PREMIUM_CUSTOMER)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

There are more Mainstream - young singles/couples and Mainstream - retirees who buy chips. This contributes to there being more sales to these customer segments but this is not a major driver for the Budget - Older families segment.

Higher sales may also be driven by more units of chips being bought per customer. Let's have a look at this next.

```{r fig.width = 10, fig.align = "center"}
#### Average number of units per customer by LIFESTAGE and PREMIUM_CUSTOMER
avg_units <- data[, .(AVG = sum(PROD_QTY)/uniqueN(LYLTY_CARD_NBR)),.(LIFESTAGE, PREMIUM_CUSTOMER)][order(-AVG)]
avg_units


ggplot(avg_units, aes(x = LIFESTAGE, y = AVG, fill = PREMIUM_CUSTOMER)) +
  geom_bar(stat = "identity", position = "dodge") +   
  labs(x = "LIFESTAGE", y = "Units per Customer", title = "Average Units per Customer by LIFESTAGE and PREMIUM_CUSTOMER") +
  theme(axis.text.x = element_text(angle = 45, hjust = .7))
```

Older families and young families in general buy more chips per customer

Let's also investigate the average price per unit chips bought for each customer segment as this is also a driver of total sales.

```{r fig.width = 10, fig.align = "center"}
#### Calculate the average price per unit sold (average sale price) 
#### by LIFESTAGE and PREMIUM_CUSTOMER

avg_price <- data[, mean(TOT_SALES/PROD_QTY), by = .(LIFESTAGE,PREMIUM_CUSTOMER)]
avg_price[order(-V1)]

ggplot(avg_price, aes(x = LIFESTAGE, y = V1, fill = PREMIUM_CUSTOMER)) +
  geom_bar(stat = "identity", position = "dodge") +   
  labs(x = "LIFESTAGE", y = "Average price per unit", 
       title = "Average price per unit chips bought by LIFESTAGE and PREMIUM_CUSTOMER") +
  theme(axis.text.x = element_text(angle = 45, hjust = .7))

```

Mainstream midage and young singles and couples are more willing to pay more per packet of chips compared to their budget and premium counterparts. This may be due to premium shoppers being more likely to buy healthy snacks and when they buy chips, this is mainly for entertainment purposes rather than their own habit of consumption. This is also supported by there being fewer premium midage and young singles and couples buying chips compared to their mainstream counterparts.

As the difference in average price per unit isn't large, we can test if this difference is statistically different.

Let mu_m be the mean unit price of mainstream midage and young singles and couples Let mu_pb be the mean unit price of premium and budget midage and young singles and couples

H0: true difference in mu_m and mu_pb is equal to 0

Ha: true difference in mu_m and mu_pb is greater than 0

```{r}
#### Perform an independent t-test between mainstream vs premium and budget midage
#### and young singles and couples

# create a new column consisting of the price for each row
pricePerUnit <- data[, price := TOT_SALES/PROD_QTY]

# Subset the data for each sample
mainstream <- pricePerUnit[PREMIUM_CUSTOMER %in% c("Mainstream") &
                           LIFESTAGE %in% c("YOUNG SINGLES/COUPLES", "MIDAGE SINGLES/COUPLES")]
other <- pricePerUnit[PREMIUM_CUSTOMER %in% c("Budget", "Premium") &
                      LIFESTAGE %in% c("YOUNG SINGLES/COUPLES", "MIDAGE SINGLES/COUPLES")]

# Perform a t-test
# t.test will take care of calculating the sample mean for each sample, 
# just input the price vector for each sample
result <- t.test(mainstream$price, other$price, alternative = "greater")
result
# Extract the p-value
p_value <- result$p.value
p_value

# # Check if the p-value is below the desired significance level (e.g., 0.05)
# if (p_value < 0.05) {
#   print("The unit price for mainstream, young and mid-age singles and couples is significantly higher.")
# } else {
#   print("The unit price for mainstream, young and mid-age singles and couples is not significantly higher.")
# }


```

The t-test results in a p-value of 3.483677e-306, i.e. the unit price for mainstream, young and mid-age singles and couples ARE significantly higher than that of budget or premium, young and midage singles and couples.

## Deep dive into specific customer segments for insights

We have found quite a few interesting insights that we can dive deeper into.

We might want to target customer segments that contribute the most to sales to retain them or further increase sales. Let's look at Mainstream - young singles/couples.

For instance, let's find out if they tend to buy a particular brand of chips compared to other segments.

```{r fig.align = "center"}
#### Deep dive into Mainstream, young singles/couples

# Are there brands that these this customer segment prefers
# more than others. 
# Could use affinity analysis or apriori analysis


# 'data' is a transactional data set where each row is a transaction


# affinity analysis

# subset two relevant groups to compare
# this is the segment of interest
segment1 <- data[PREMIUM_CUSTOMER == "Mainstream" &
                 LIFESTAGE == "YOUNG SINGLES/COUPLES", ]
# the rest of population serves as the baseline comparison
Other <- data[!(PREMIUM_CUSTOMER == "Mainstream" &
                 LIFESTAGE == "YOUNG SINGLES/COUPLES"), ]

# how many units did segment1 buy?
quantity_segment1 <- segment1[, sum(PROD_QTY)]
# how many units did the rest buy?
quantity_other <- Other[, sum(PROD_QTY)]

# calculate proportion that bought a specific brand by segment1
quantity_segment1_byBrand <- segment1[, .(TargetSeg = sum(PROD_QTY)/quantity_segment1), by = BRAND]
# calculate proportion that bought a specific brand by the rest of the population
quantity_Other_byBrand <- Other[, .(otherSegs = sum(PROD_QTY)/quantity_other), by = BRAND]

# calculate and compare to see which brands segment1 particularly tends to buy compared to other segments.
brand_proportions <- merge(quantity_segment1_byBrand,quantity_Other_byBrand)[, AffinityToBrand := TargetSeg/otherSegs] 
brand_proportions[order(-AffinityToBrand)]


```

We can see that :

-   Mainstream young singles/couples are 23% more likely to purchase Tyrrells chips compared to the rest of the population

-   Mainstream young singles/couples are 56% less likely to purchase Burger Rings compared to the rest of the population

Let's also find out if our target segment tends to buy larger packs of chips.

```{r fig.align = "center"}
#### Preferred pack size compared to the rest of the population

# Over to you! Do the same for pack size.
# calculate proportion that bought a specific brand by segment1
quantity_segment1_byPackSize <- segment1[, .(TargetSeg = sum(PROD_QTY)/quantity_segment1), by = PACK_SIZE]
# calculate proportion that bought a specific brand by the rest of the population
quantity_Other_byPackSize <- Other[, .(otherSegs = sum(PROD_QTY)/quantity_other), by = PACK_SIZE]

# calculate and compare to see which brands segment1 particularly tends to buy compared to other segments.
packSize_proportions <- merge(quantity_segment1_byPackSize,quantity_Other_byPackSize)[, AffinityToPack := TargetSeg/otherSegs] 
packSize_proportions[order(-AffinityToPack)]


```

-   Mainstream young singles/couples are 27% more likely to purchase pack size of 270g compared to the rest of the population

-   Mainstream young singles/couples are 56% less likely to purchase pack size of 220g compared to the rest of the population

Let's dive into what brands sell this pack size.

```{r}
data[PACK_SIZE == 270, unique(PROD_NAME)]

```

Twisties is the only brand that offers 270g pack size. This brand also comes in 2nd in our Brand Affinity analysis. This contributes to why our target segment buys a lot of this pack size.

## Conclusion

Let's recap what we've found! This may serve as a precursor to more formal testing and analysis.

-   Sales have mainly been due to Budget - older families, Mainstream - young singles/couples, and Mainstream - retirees shoppers.
-   Although Budget - older families accounts for the largest proportion of sales (8.7%), the amount of customers in this segment (6.5%) is not as great as the Mainstream - young singles/couples (11.1%) and Mainstream - retirees shoppers (8.9%)
-   This implies the sales can be further improved in the two Mainstream - young singles/couples and Mainstream - retirees shoppers segments
-   We also found out the Mainstream - young singles/couples are among the segments that bought the least units of chips per customer. However, they are willing to spend the most on chips.
-   Notable mention is Mainstream - young singles/couples, who are also willing to spend more on chips than others.
-   This implies that the Mainstream - young singles/couples prefer higher quality chips and/or more popular brands. Their most preferred brands are Tyrrells, Twisties, Doritos, Kettle, and Tostitos
-   Mainstream young singles/couples are 27% more likely to purchase pack size of 270g
-   270g seems to be the ideal pack size for Mainstream young singles/couples. However, the only brand that provides this pack size is Twisties in this store. Perhaps, including more brands with 270g pack size is a potential step towards more sales.
-   Overall, we suggest an emphasis on the Mainstream - young singles/couples. One suggestion would be to have some Tyrrells chips near areas in the store that this target segment tends to visit the most.
